---
title: "HPV Project"
author: "Hong and Moiyyad"
date: "2024-10-28"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Our Assumption

```{r,warning=FALSE,message=FALSE,echo=FALSE}
library(DiagrammeR)
library(dagitty)
library(lavaan)
library(ggdag)
library(ggformula)
library(caret)
library(cowplot)
library(tidyverse)
library(foreign)
library(Hmisc)
library(survey)
theme_set(theme_bw())
MyPlot<-dagitty('
  dag {
    Age 
    Gender 
    Race 
    Income 
    HepatitisB_Vaccine
    PastInfection 
    Immunity 
    ForeignCountryExp 
    BornCountry
    BloodTransfusion
    LiverDisease
    
    Age -> HepatitisB_Vaccine
    Gender -> HepatitisB_Vaccine
    Race -> HepatitisB_Vaccine
    Income -> HepatitisB_Vaccine
    
    
    HepatitisB_Vaccine -> Immunity
    Immunity -> PastInfection
    ForeignCountryExp -> PastInfection
    BornCountry -> PastInfection
    BloodTransfusion -> PastInfection
    LiverDisease -> PastInfection
    
}',layout = TRUE)
plot(MyPlot)
```

## Predictive Model

We will use *Immunity*,*PastInfection*,*ForeignCountryExp*,*BornCountry*,*BloodTransfusion*,*LiverDisease* as predictors to predict whether *PastInfection* or not.

- Immunity: we will use predicted immunity to replace the missing values in **LBXHBS** (Hepatitis B Surface Antibody);the hepatitis B surface antibody (anti-HBs) demonstrates immunity acquired through vaccination.  
- BloodTransfusion: indicated by **MCQ092** (Ever received blood transfusion);
- ForeignCountryExp: indicated by **DMQADFC** (Whether served in a foreign country).
- BornCountry: indicated by **DMDBORN4** (Born Country).
- LiverDisease: indicated by **MCQ160L** (Ever told you had any liver condition (for age>-20))

- PastInfection: indicated by **LBDHBC** (Hepatitis B Core Antigen) or **MCQ160L** (Ever told you had any liver condition)

- CurrentInfection: indicated by **LBDHBG** (Hepatitis B Surface Antigen). Number of Non-Missing is 402. of Missing observations. For these participants with non-missing LBDHBG (31 Positive, 375 Negative), they all had past infection experience indicated by **LBXHBC** (Hepatitis B Core Antibody). 

```{r,warning=FALSE,message=FALSE,echo=FALSE}
PredictivePlot<-dagitty('
  dag {
    Immunity 
    ForeignCountryExp 
    BornCountry
    PastInfection
    BloodTransfusion
    LiverDisease
   
    Immunity -> PastInfection
    BornCountry -> PastInfection
    ForeignCountryExp -> PastInfection
    BloodTransfusion -> PastInfection
    LiverDisease -> PastInfection
    
}',layout = TRUE)
plot(PredictivePlot)
```


## Our DataSet

We merged several dataset: 

- DEMO_J.XPT (Demographic dataset);   
- HEPB_S_J.XPT (immunization dataset); 
- HEPBD_J.XPT (Blood test dataset);
- HEQ_J.XPT (Hepatitis questionare dataset); 
- IMQ_J.XPT (vaccine dataset); 
- MCQ_J.XPT (Medical condition dataset).

```{r,echo=FALSE}
Demographic<-read.xport("DEMO_J.XPT")
Demographic<-Demographic[,c("SEQN","DMDBORN4","DMQADFC","INDFMIN2","RIAGENDR","RIDAGEYR","RIDRETH3",
                            "WTINT2YR","WTMEC2YR","SDMVPSU","SDMVSTRA")]
Demographic$RIDRETH3<-factor(Demographic$RIDRETH3,levels = c(1,2,3,4,6,7),
                             labels = c("Mexican American","Other Hispanic","Non-Hispanic White","Non-Hispanic Black","Non-Hispanic Asian","Non-Hispanic Others"))
Demographic$DMQADFC<-factor(Demographic$DMQADFC,levels = c(1,2,7,9),labels = c("Yes","No","Refused","Dont Know"))
Demographic$DMDBORN4<-factor(Demographic$DMDBORN4,levels = c(1,2,77,99),labels = c("Born in US","Others","Refused","Dont Know"))
Demographic$INDFMIN2<-factor(Demographic$INDFMIN2,levels = sort(unique(Demographic$INDFMIN2)),
                             labels = c("$0-$4999","$5000-9999","$10,000-14,999","$15,000-19,999","$20,000-24,999",
                                        "$25,000-34,999","$35,000-44,999","$45,000-54,999","$55,000-64,999","$65,000-74,999",
                                        "$20,000 and over","Under $20,000","75,000-99,999","$100,000 and Over","Refused","Dont Know"))
Demographic$RIAGENDR<-factor(Demographic$RIAGENDR,levels = c(1,2),labels = c("Male","Female"))


###Lots of Missing in Drug Use
# DrugUse<-read.xport("DUQ_J.XPT")

###Examined participants aged 2 years and older were eligible.
HBV_SurfaceAntibody<-read.xport("HEPB_S_J.XPT")
HBV_SurfaceAntibody$LBXHBS<-factor(HBV_SurfaceAntibody$LBXHBS,levels = c(1,2,3),labels = c("Positive","Negative","Indeterminate"))

###Examined participants aged 6 years or older were eligible.
HBV_CoreAntibody<-read.xport("HEPBD_J.XPT")
HBV_CoreAntibody<-HBV_CoreAntibody[,c("SEQN","LBXHBC","LBDHBG")]
HBV_CoreAntibody$LBXHBC<-factor(HBV_CoreAntibody$LBXHBC,levels = c(1,2,3),labels = c("Positive","Negative","Indeterminate"))
HBV_CoreAntibody$LBDHBG<-factor(HBV_CoreAntibody$LBDHBG,levels = c(1,2,3),labels = c("Positive","Negative","Indeterminate"))

###The Hepatitis questionnaire (variable name prefix HEQ) provides respondent-level interview data on previous 
###diagnosis of hepatitis B and hepatitis C and, among participants reporting a previous diagnosis, reported 
###prescription medication treatment. Participants aged 6 years and over were eligible.
Hepatitis<-read.xport("HEQ_J.XPT")
Hepatitis<-Hepatitis[,c("SEQN","HEQ010","HEQ020")]
Hepatitis$HEQ010<-factor(Hepatitis$HEQ010,levels = c(1,2,7,9),labels = c("Yes","No","Refused","Dont Know"))
Hepatitis$HEQ020<-factor(Hepatitis$HEQ020,levels = c(1,2,7,9),labels = c("Yes","No","Refused","Dont Know"))

Hepatitis_Dat<-left_join(full_join(HBV_SurfaceAntibody,HBV_CoreAntibody,by = "SEQN"),Hepatitis,by = "SEQN")
rm(HBV_CoreAntibody,HBV_SurfaceAntibody,Hepatitis)


###Participants aged 2 years and older were asked about the hepatitis A vaccination; all participants were asked 
###about the hepatitis B vaccination; and participants 9 to 59 years of age were asked about the HPV vaccination.
Immunization<-read.xport("IMQ_J.XPT")
Immunization<-Immunization[,c("SEQN","IMQ011","IMQ020")]
Immunization$IMQ011<-factor(Immunization$IMQ011,levels = c(1,2,3,7,9),
                            labels = c("Yes,at least 2 doses","Less than 2 doses","No doses","Refused","Dont Know"))
Immunization$IMQ020<-factor(Immunization$IMQ020,levels = c(1,2,3,7,9),
                            labels = c("Yes,at least 2 doses","Less than 2 doses","No doses","Refused","Dont Know"))


Med_Dat<-left_join(Immunization,Hepatitis_Dat,by = "SEQN")
rm(Immunization,Hepatitis_Dat)

MedicalCondition_Dat<-read.xport("MCQ_J.XPT")
MedicalCondition_Dat<-MedicalCondition_Dat[,c("SEQN","MCQ092","MCQ160L","MCQ170L","MCQ500")]
MedicalCondition_Dat$MCQ092<-factor(MedicalCondition_Dat$MCQ092,levels = c(1,2,7,9),labels = c("Yes","No","Refused","Dont Know"))
MedicalCondition_Dat$MCQ160L<-factor(MedicalCondition_Dat$MCQ160L,levels = c(1,2,9),labels = c("Yes","No","Dont Know"))
MedicalCondition_Dat$MCQ170L<-factor(MedicalCondition_Dat$MCQ170L,levels = c(1,2,9),labels = c("Yes","No","Dont Know"))
MedicalCondition_Dat$MCQ500<-factor(MedicalCondition_Dat$MCQ500,levels = c(1,2),labels = c("Yes","No"))
Med_Dat<-left_join(Med_Dat,MedicalCondition_Dat,by = "SEQN")
FullDat<-full_join(Demographic,Med_Dat,by = "SEQN")
rm(Med_Dat,Demographic,MedicalCondition_Dat)


col_labels<-c(SEQN="ID",
              DMDBORN4="Born Country",
              DMQADFC="Sever in a foreign country",INDFMIN2="Family Income",
              RIAGENDER="Gender",RIDAGEYR="Age(0-80)",
              RIDRETH3="Race(Six Categories Including Non-Hispanic Asian)",
              WTINT2YR="Full Sample 2 year interview weight",WTMEC2YR="Full Sample 2 year MEC exam weight",
              SDMVPSU="Masked variance pseudo-PSU",SDMVSTRA="Masked variance pseudo-stratum",
              IMQ011="Hepatitis A Vaccine",IMQ020="Hepatitis B 3 dose",
              LBXHBS="Hepatitis B Surface Antibody",LBXHBC="Hepatitis B Core Antibody",LBDHBG="Hepatitis B Surface Antigen",
              HEQ010="Ever told you have Hepatitis B",HEQ020="Ever prescribed meds treat Hepatitis B",
              MCQ092="Ever received blood transfusion",
              MCQ160L="Ever told you had any liver condition (for age>=20)",
              MCQ170L="Do you still have a liver condition (for age >=20)",
              MCQ500="Ever told you had any liver condition (for age 12-19 years)")
label(FullDat)<-as.list(col_labels[match(names(FullDat),names(col_labels))])
colnames(FullDat)<-paste(colnames(FullDat),col_labels,sep = ":")
#write_xlsx(FullDat,"Hepatitis project dataset.xlsx")
rm(col_labels)
FullDat[,"WhetherVaccine"]<-1
FullDat[which(FullDat$`IMQ020:Hepatitis B 3 dose`=="No doses"),"WhetherVaccine"]<-0

FullDat$`DMQADFC:Sever in a foreign country`<-as.character(FullDat$`DMQADFC:Sever in a foreign country`)
FullDat[is.na(FullDat$`DMQADFC:Sever in a foreign country`),"DMQADFC:Sever in a foreign country"]<-"No"
FullDat[which(FullDat$`DMQADFC:Sever in a foreign country`=="Refused"),"DMQADFC:Sever in a foreign country"]<-"No"
FullDat$`DMQADFC:Sever in a foreign country`<-as.factor(FullDat$`DMQADFC:Sever in a foreign country`)
FullDat$`DMDBORN4:Born Country`<-as.character(FullDat$`DMDBORN4:Born Country`)
FullDat[which(FullDat$`DMDBORN4:Born Country`%in%c("Refused","Dont Know")),"DMDBORN4:Born Country"]<-"Others"
FullDat$`DMDBORN4:Born Country`<-as.factor(FullDat$`DMDBORN4:Born Country`)
FullDat$`MCQ092:Ever received blood transfusion`<-as.character(FullDat$`MCQ092:Ever received blood transfusion`)
FullDat[which(FullDat$`MCQ092:Ever received blood transfusion`%in%c("Refused","Dont Know")),"MCQ092:Ever received blood transfusion"]<-"No"
FullDat[is.na(FullDat$`MCQ092:Ever received blood transfusion`),"MCQ092:Ever received blood transfusion"]<-"No"
FullDat$`MCQ092:Ever received blood transfusion`<-as.factor(FullDat$`MCQ092:Ever received blood transfusion`)
FullDat$`MCQ160L:Ever told you had any liver condition (for age>=20)`<-as.character(FullDat$`MCQ160L:Ever told you had any liver condition (for age>=20)`)
FullDat[which(FullDat$`MCQ160L:Ever told you had any liver condition (for age>=20)`=="Dont Know"),"MCQ160L:Ever told you had any liver condition (for age>=20)"]<-"No"
FullDat[is.na((FullDat$`MCQ160L:Ever told you had any liver condition (for age>=20)`)),"MCQ160L:Ever told you had any liver condition (for age>=20)"]<-"No"
FullDat$`MCQ160L:Ever told you had any liver condition (for age>=20)`<-as.factor(FullDat$`MCQ160L:Ever told you had any liver condition (for age>=20)`)

FullDat[is.na(FullDat$`INDFMIN2:Family Income`),"INDFMIN2:Family Income"]<-"$45,000-54,999"
FullDat[which(FullDat$`INDFMIN2:Family Income`%in%c("Refused","Dont Know")),"INDFMIN2:Family Income"]<-"$45,000-54,999"
FullDat[,"FamilyIncome_Low"]<-0
FullDat[which(FullDat$`INDFMIN2:Family Income`%in%c("$0-$4999","$5000-9999","$10,000-14,999","Under $20,000")),"FamilyIncome_Low"]<-1
FullDat[,"FamilyIncome_Medium"]<-0
FullDat[which(FullDat$`INDFMIN2:Family Income`%in%c("$25,000-34,999","$35,000-44,999","$45,000-54,999","$55,000-64,999",
                                                    "$20,000 and over")),"FamilyIncome_Medium"]<-1

FullDat<-FullDat[which(FullDat$`LBXHBC:Hepatitis B Core Antibody`%in%c("Positive","Negative")),]
```


## Survey Design

```{r}
HepatitisB_svyd<-svydesign(data = FullDat,ids = ~`SDMVPSU:Masked variance pseudo-PSU`,
                           strata = ~`SDMVSTRA:Masked variance pseudo-stratum`,
                           weights = ~`WTMEC2YR:Full Sample 2 year MEC exam weight`,
                           nest = TRUE)
Means<-svymean(~`LBXHBC:Hepatitis B Core Antibody`,HepatitisB_svyd)
barplot(Means)
```


### Step 1: The probability for a participant taking the HBV

$log\frac{P(Vaccine=Yes|Age,Race,Gender,Income)}{P(Vaccine=No|Age,Race,Gender,Income)}=b_0+b_1*Age+b_2*Race+b_3*Gender+b_4*Income$

```{r,warning=FALSE,message=FALSE,echo=FALSE}
P1<-svydesign(ids = ~`SDMVPSU:Masked variance pseudo-PSU`,
              strata = ~`SDMVSTRA:Masked variance pseudo-stratum`,
              weights = ~`WTMEC2YR:Full Sample 2 year MEC exam weight`,
              data = FullDat,
              nest = TRUE)
P1_Model<-svyglm(formula = WhetherVaccine~`RIDAGEYR:Age(0-80)`+`RIAGENDR:Gender`+`RIDRETH3:Race(Six Categories Including Non-Hispanic Asian)`+FamilyIncome_Low+FamilyIncome_Medium,
                 design = P1,family = quasibinomial())
summary(P1_Model)
FullDat[,"Predicted_Pro_Vaccine"]<-predict.glm(P1_Model,type = "response")
FullDat[,"WhetherVaccine"]<-1
FullDat[which(FullDat$`IMQ020:Hepatitis B 3 dose`=="No doses"|FullDat$Predicted_Pro_Vaccine<0.5),"WhetherVaccine"]<-0
FullDat$WhetherVaccine<-as.factor(FullDat$WhetherVaccine)
gf_bar(~WhetherVaccine,data = FullDat)

FullDat[,"VaccineDoses"]<-0
FullDat[which(FullDat$`IMQ020:Hepatitis B 3 dose`=="Less than 2 doses"),"VaccineDoses"]<-1
FullDat[which(FullDat$`IMQ020:Hepatitis B 3 dose`=="Yes,at least 2 doses"),"VaccineDoses"]<-2
FullDat$VaccineDoses<-factor(FullDat$VaccineDoses,levels = c(0,1,2),
                             labels = c("No doses","1 dose","2 or 3 doses"))   
gf_bar(~VaccineDoses,data = FullDat)
```

The sample size used to predict WhetherVaccineOrNot is `r dim(FullDat)[1]`. Masked Variance weights (SDMVPSU and SDMVSTRA) and Full Sample 2 year MEC weight (WTMEC2YR) are used in svyglm function.

Original Variable "IMQ020: Hepatitis B 3 dose", if "Refused" or "Dont Know" or "Missing", use predicted_probability to impute values. If the predicted_probability in Step 1 is larger than 0.5, classify the participants to "1 dose", below than 0.5, classify the participants to "0 dose".

### Step 2:

Step 2: The probability for a participant getting immunity through the HBV.

$log\frac{P(Immunity=Yes|VaccineDoses))}{P(Immunity=No|VaccineDoses)}=\beta_0 +\beta_1*VaccineDoses$

```{r,echo=FALSE,message=FALSE,warning=FALSE}
SampleSize_P2<-length(which(is.na(FullDat$`LBXHBS:Hepatitis B Surface Antibody`)==FALSE))
WhichComplete_P2<-which(is.na(FullDat$`LBXHBS:Hepatitis B Surface Antibody`)==FALSE)
P2<-svydesign(ids = ~`SDMVPSU:Masked variance pseudo-PSU`,
              strata = ~`SDMVSTRA:Masked variance pseudo-stratum`,
              weights = ~`WTMEC2YR:Full Sample 2 year MEC exam weight`,
              data = FullDat,
              nest = TRUE)
P2_Model<-svyglm(formula = `LBXHBS:Hepatitis B Surface Antibody`~ VaccineDoses,
                 design = P2,family = quasibinomial())
summary(P2_Model)
FullDat[WhichComplete_P2,"Predicted_Pro_Immunity"]<-predict.glm(P2_Model,type = "response")
df_stats(~Predicted_Pro_Immunity,data = FullDat[WhichComplete_P2,],min,max,mean,sd)
```

The sample size used to predict WhetherImmunityOrNot is `r SampleSize_P2`. Masked Variance weights (SDMVPSU and SDMVSTRA) and Full Sample 2 year MEC weight (WTMEC2YR) are used in svyglm function.


### Step 3: Predictive Model 

$log(\frac{P(PastInfection=Yes)}{P(PastInfection=No)}=B_0+B_1*ImmunityProb+B_2*ForeignCountryExp+B_3*BornCountry+B_4*BloodsTranfusion$
       
```{r,echo=FALSE,message=FALSE,warning=FALSE}
WhichComplete_P3<-intersect(intersect(which(!is.na(FullDat$`LBXHBC:Hepatitis B Core Antibody`)),which(!is.na(FullDat$Predicted_Pro_Immunity))),which(!is.na(FullDat$`MCQ160L:Ever told you had any liver condition (for age>=20)`)))
SampleSize_P3<-length(WhichComplete_P3)
FullDat$`LBXHBC:Hepatitis B Core Antibody`<-as.character(FullDat$`LBXHBC:Hepatitis B Core Antibody`)
FullDat$`LBXHBC:Hepatitis B Core Antibody`<-factor(FullDat$`LBXHBC:Hepatitis B Core Antibody`,levels = c("Positive","Negative"))
#table(P3_Dat$`LBXHBC:Hepatitis B Core Antibody`)
P3<-svydesign(ids = ~`SDMVPSU:Masked variance pseudo-PSU`,
              strata = ~`SDMVSTRA:Masked variance pseudo-stratum`,
              weights = ~`WTMEC2YR:Full Sample 2 year MEC exam weight`,
              data = FullDat,
              nest = TRUE)
P3_Model<-svyglm(formula = `LBXHBC:Hepatitis B Core Antibody`~Predicted_Pro_Immunity+`DMQADFC:Sever in a foreign country`+`DMDBORN4:Born Country`+
                   `MCQ092:Ever received blood transfusion`+`MCQ160L:Ever told you had any liver condition (for age>=20)`,
                 design = P3,family = quasibinomial())
summary(P3_Model)

MyPredictors<-cbind(rep(1,SampleSize_P3),FullDat$Predicted_Pro_Immunity[WhichComplete_P3],FullDat$`DMQADFC:Sever in a foreign country`[WhichComplete_P3],FullDat$`DMDBORN4:Born Country`[WhichComplete_P3],FullDat$`MCQ092:Ever received blood transfusion`[WhichComplete_P3],FullDat$`MCQ160L:Ever told you had any liver condition (for age>=20)`[WhichComplete_P3])
MyCoefficents<-matrix(coef(P3_Model))
FullDat[WhichComplete_P3,"Predicted_Pro_PastInfection"]<-1-1/(1+exp(-MyPredictors%*%MyCoefficents))
Validity<-FullDat[!is.na(FullDat$Predicted_Pro_PastInfection),]
CutOff<-seq(min(Validity$Predicted_Pro_PastInfection),max(Validity$Predicted_Pro_PastInfection),length.out=100)
DecisionCri<-data.frame()
for(CutOff_value in CutOff){
  Validity[,"Predicted_PastInfection"]<-"Negative"
  Validity[which(Validity$Predicted_Pro_PastInfection>CutOff_value),"Predicted_PastInfection"]<-"Positive"
  Validity$Predicted_PastInfection<-factor(Validity$Predicted_PastInfection,levels = c("Positive","Negative"))
  Validity_Current<-Validity[!is.na(Validity$`LBDHBG:Hepatitis B Surface Antigen`),]
  Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`<-as.character(Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`)
  Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`<-factor(Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`,levels = c("Positive","Negative"))
  Result<-confusionMatrix(data = Validity$Predicted_PastInfection,reference=Validity$`LBXHBC:Hepatitis B Core Antibody`)
  Result_Current<-confusionMatrix(data = Validity_Current$Predicted_PastInfection,reference = Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`)
  DecisionCri<-rbind(DecisionCri,
                     c(CutOff_value,Result$overall["Accuracy"],Result$byClass[c("Sensitivity","Specificity")],
                       Result_Current$overall["Accuracy"],Result_Current$byClass[c("Sensitivity","Specificity")]))
  colnames(DecisionCri)<-c("CutOff",
                           "Accuracy(PastInfection)","Sensitivity(PastInfection)","Specificity(PastInfection)",
                           "Accuracy(CurrentInfection)","Sensitivity(CurrentInfection)","Specificity(CurrentInfection)")
}
plot_dat<-data.frame(CutOff=rep(DecisionCri$CutOff,6),
                     Values=c(DecisionCri$`Accuracy(PastInfection)`,DecisionCri$`Sensitivity(PastInfection)`,DecisionCri$`Specificity(PastInfection)`,
                              DecisionCri$`Accuracy(CurrentInfection)`,DecisionCri$`Sensitivity(CurrentInfection)`,DecisionCri$`Specificity(CurrentInfection)`),
                     Type=rep(rep(c("Accuracy","Sensitivity","Specificity"),each=length(DecisionCri$CutOff)),2),
                     Status=rep(c("PastInfection","CurrentInfection"),each=length(DecisionCri$`Accuracy(CurrentInfection)`)*3))
plot_dat$Type<-as.factor(plot_dat$Type)
plot_dat$Status<-as.factor(plot_dat$Status)
gf_line(Values~CutOff,data = plot_dat,color = ~Status)%>%
  gf_facet_wrap(~Type)%>%
  gf_labs(x="Cut-off Probability for PastInfection",y="Rate")%>%
  gf_theme(legend.position="bottom")  

OurCut<-1-length(which(FullDat$`LBDHBG:Hepatitis B Surface Antigen`=="Positive"))/(length(which(FullDat$`LBDHBG:Hepatitis B Surface Antigen`%in%c("Positive","Negative"))))
Validity[,"Predicted_PastInfection"]<-"Negative"
Validity[which(Validity$Predicted_Pro_PastInfection>OurCut),"Predicted_PastInfection"]<-"Positive"
Validity$Predicted_PastInfection<-factor(Validity$Predicted_PastInfection,levels = c("Positive","Negative"))
Validity_Current<-Validity[!is.na(Validity$`LBDHBG:Hepatitis B Surface Antigen`),]
Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`<-as.character(Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`)
Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`<-factor(Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`,levels = c("Positive","Negative"))
Our_Current<-confusionMatrix(data = Validity_Current$Predicted_PastInfection,reference = Validity_Current$`LBDHBG:Hepatitis B Surface Antigen`)
```
     